### 2022-12-07 editorial-communication/response-to-the-reviewers.Rmd

As a long-term but sporadic GitHub user myself, I agree with most of the points and cases presented in the paper.

**E1.1.** I agree with Reviewer 1 that these could be streamlined somewhat into a smaller number of more generalizable cases. They also are a bit heavily weighted towards more experienced users. "Simple" operations like push, pull, and commit are rarely understandable to new users, who routinely forget to commit their actions. The GitHub Desktop app makes many of the operations and use of GitHub somewhat easier, and is a good entree into GitHub and Git for novices. More could be made of the desktop app.

**E1.2.** In my own experience, the "public" nature of repos is a major barrier to the use of GitHub for exactly the reason you suggest - EEB practioners remain very uncomfortable with sharing data pre-publication (and often even post-publication). Some additional emphasis on the ability to make repos "private" should be included beyond the Boxes.

We now directly discuss the possibility of keeping repositories private in the section "Storing and sharing research compendia" and in the "Open science discussion" to emphasize that there is not necessarily a trade-off between privacy, collaboration, and open science practices.

@@

**R2.1.** Figure 1 was more confusing to me than helpful. It presents a view of a Github interface in order to detail generalized features; however, it is edited/abstracted so much that it doesn't map easily to the interface as it would be viewed by a reader of the paper. To improve this I would reduce the level of abstraction of the web interface.

**R2.2.** Figure 2 was useful, especially as it summarized across multiple areas that a reader make in-roads into using Github. Please clarify how the "Technical Difficulty" was assessed. Was this based on the impression of the working group? Was it quantified using different types of required knowledge (e.g., programming, software design, working in the Terminal, etc.)?

**R2.3.** I would find it helpful to give a brief (1-2 sentence) history of Git (L85-89). Namely, that it was developed as an aid for software development within distributed groups of software engineers and was developed within an open-source framework so that it could be improved by the community. This provides more context as to why Github (as it extends Git) is a useful tool for collaboration "by design".

We now briefly discuss the origin of Git and its expansion to applications beyond software development to help manage collaborations and community contributions, in the introduction.

### 2022-12-07 manuscript.tex
Merge pull request #296 from SORTEE-Github-Hackathon/phpb-addressing-git-issue-284 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/58a2b25be4b30ef82f1ebbb07581893859ebcd27.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/58a2b25be4b30ef82f1ebbb07581893859ebcd27/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3640990890

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8f400dd0f6c28e752d4f7127284c1a33f564d2a1/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8f400dd0f6c28e752d4f7127284c1a33f564d2a1}{SORTEE-Github-Hackathon/manuscript@8f400dd}
on December 7, 2022.

@@

Git is the version control system that enables all the collaborative tools available on GitHub.
Although the understanding of basic concepts of Git (such as commit, push, pull, checkout; see \protect\hyperlink{definitions}{Box 1}) is necessary, the GitHub web-based platform and its integrated development environments (such as the GitHub Desktop) allow users to perform most repository and data management operations without opening Git command-line sessions.

@@

@@

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/58a2b25be4b30ef82f1ebbb07581893859ebcd27/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/58a2b25be4b30ef82f1ebbb07581893859ebcd27}{SORTEE-Github-Hackathon/manuscript@58a2b25}
on December 7, 2022.

@@

Git is the version control system that enables all the collaborative tools available on GitHub.
Git was originally developed as a fast, lightweight and open-source system that would allow software engineers to efficiently develop and collaborate in projects (\protect\hyperlink{ref-1CM2EcdVk}{\emph{Git - A Short History of Git}, n.d.}\#:\textasciitilde:text=A\%20Short\%20History\%20of\%20Git\%20As\%20with\%20many,were\%20passed\%20around\%20as\%20patches\%20and\%20archived\%20files.).
Since its launch in 2005, Git has become the leading version control system in software development and in other disciplines that similarly require collaboration and community contributions, such as scientific research (\protect\hyperlink{ref-7q3wZN6d}{Spinellis, 2012}).
Although the understanding of basic concepts of Git (such as commit, push, pull, checkout; see \protect\hyperlink{definitions}{Box 1}) is necessary, the GitHub web-based platform and its integrated development environments (such as GitHub Desktop) allow users to perform most repository and data management operations without opening Git command-line sessions, making these functionalities available to users who are less familiar with software development.

@@

\leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
\emph{Git - A Short History of Git}. (n.d.). Retrieved December 7, 2022, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}

@@

\leavevmode\vadjust pre{\hypertarget{ref-7q3wZN6d}{}}%
Spinellis, D. (2012). Git. \emph{IEEE Software}, \emph{29}(3), 100--101. \url{https://doi.org/10.1109/ms.2012.61}
